Lyman-$\alpha$ photons through rotating outflows

### 2018-03-31 paper/paper.tex
edit

In Figure \ref{fig:doppler} we present a toy model for the spectrum of
a LAE taken from to different sides of the galaxy. 
As the LAE is rotating, one side is being redshifted while the other
is blueshifted. 
We see that the full spectrum is a weighted line, in solid black,
that is found between these two.
In this toy model the rotational velocity is \vrot$=100\ \kms$. 
We highlight that the distance between the maxima of the blue and red
spectra is not twice the rotational velocity as it could be naively
expected.
Although the spectra can be modeled by Doppler shifts, the peak of the
spectra is also weighted by the amount of mass that has a given
velocity. 
In this toy model

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{./figures/discussion/doppler}
  \end{center}
  \caption{\textbf{Doppler Shift:} We fix $\vout=25$\kms, $\vrot=100$\kms, $\tauh=10^5$.
    \label{fig:doppler}}
\end{figure}

@@

\subsection{Application to observational data}

We find three different approaches how this model can have observational
implications. Firstly,

>>>>

In Figure \ref{fig:doppler} we present a toy model (\vrot$=50\ \kms$,
\vout$=25\ \kms$ and \tauh$=10^5$) for the spectrum of
a LAE taken from to different sides of the galaxy. 
As the LAE is rotating, one side is being redshifted while the other
is blueshifted. 
We see that the full spectrum is a weighted line, in solid black,
that is found between these two.
We notice that the distance between the maxima of the blue and red
spectra is not twice the rotational velocity as it could be naively
expected.
Although is a good approximation to model the rotating spectra by a
sum of Doppler shifts, the peak of the spectra is also weighted by the
amount of mass with a given velocity. 
In this toy model the distance between the peaks of the
receeding/approaching spectra is close to $\sim 20\ \kms$, which is
less than half of the naively expected value of $2\vrot=100\ \kms$

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{./figures/discussion/doppler}
  \end{center}
  \caption{\textbf{Spectra from receeding/approaching sides of a toy
      model LAE.}  These results correspond to the RT simulation with
    $\vout=25$\kms, $\vrot=50$\kms, $\tauh=10^5$. 
    The spectra were computed for a viewing angle of
    $\theta=90^{\circ}$. 
    \label{fig:doppler}}
\end{figure}

@@
